IML Term project paper

### 2022-12-23 paper.rmd
Update paper.rmd

In order to reduce knitting time for the file, we will in this report instead of expressing the full R code to calculate the values, simply report the results we received. The results for the two-class models in terms of loo-cross-validated accuracy and perplexity are:
\begin{table}
\begin{tabular}{|r|ccc|}
\hline
Model type & Loo-CV accuracy & Loo-CV perplexity&Binary accuracy on test data\\
\hline
Dummy model & 0 & 2.01&\\
Logistic regression & 0.87 & 1.36&0.84\\
Naive Bayes & 0.81 & 152.85&\\
LDA & 0.89 & 1.33&\\
QDA & 0.85 & 6.34&\\
SVM & 0.88 & 1.34&0.84\\
Lasso & 0.89 & 1.29&0.87\\
Random Forest & 0.89 & 1.35&\\
\hline
\end{tabular}
\end{table}

>>>>

In order to reduce knitting time for the file, we will in this report instead of expressing the full R code to calculate the values, simply report the results we received. The results for the two-class models in terms of loo-cross-validated accuracy and perplexity are:
\begin{table}
\begin{tabular}{|r|ccc|}
\hline
Model type & Loo-CV accuracy & Loo-CV perplexity&Binary accuracy on test data\\
\hline
Dummy model & 0 & 2.01&\\
Logistic regression & 0.87 & 1.36&0.84\\
Naive Bayes & 0.81 & 152.85&\\
LDA & 0.89 & 1.33&\\
QDA & 0.85 & 6.34&\\
SVM & 0.88 & -&0.84\\
Lasso & 0.89 & 1.29&0.87\\
Random Forest & 0.89 & 1.35&\\
\hline
\end{tabular}
\end{table}
